\tableofcontents
\pagenumbering{roman}
\begin{titlepage}
\setlength\parindent{0pt}
\addcontentsline{toc}{section}{\numberline{}{\bf Title Page}}
\begin{center}
	\textbf{\large THE COMPARISON OF GAUSSIAN ELIMINATION AND CHOLESKY DECOMPOSITION METHODS TO LINEAR SYSTEM OF EQUATIONS}
\end{center}
\vspace{0.6in}
\begin{center}
	BY
\end{center}
\vspace{0.6in}
\begin{center}
	\textbf{ODEBUNMI, Opeyemi Muhammed}
	\\[35pt]
	
	 MATRIC NUMBER: 16/56EB110
\end{center}
\vspace{2cm}
A PROJECT SUBMITTED TO THE DEPARTMENT OF MATHEMATICS, FACULTY OF PHYSICAL SCIENCES, UNIVERSITY OF ILORIN, ILORIN, NIGERIA.\\
 IN PARTIAL FULFILLMENT OF  REQUIREMENTS FOR THE AWARD OF BACHELOR OF SCIENCE (B.Sc) DEGREE IN MATHEMATICS.
\\[35pt]
\begin{center}
JUNE, 2021.
\end{center}
\end{titlepage}

\pagenumbering{roman}
\newpage
\begin{center}\section*{Certification}\end{center}
This is to certify that this project work was carried out by \textbf{ODEBUNMI, Opeyemi Muhammed} with matriculation number \textbf{16/56EB110} and approved as meeting the requirement for the Award of Bachelor of Science (B. Sc.) Degree in the Department of Mathematics, Faculty of Physical Sciences, University of Ilorin, Ilorin, Nigeria.\\

\vspace{.99in}
\noindent
\dotfill			\hfill			\dotfill\\
{Dr. O. T. Olotu} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  Date\\
Supervisor

\vspace{.99in}
\noindent
\dotfill			\hfill			\dotfill\\
{Prof. K. Rauf} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ Date\\
Head of Department

\vspace{.99in}
\noindent
\dotfill			\hfill			\dotfill\\
{Prof. T. O. Oluyo} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  Date\\
External Examiner

\newpage
\section*{\begin{center}Dedication\end{center}}
This project is dedicated to the King of kings, Lord of lords and God of Universe, the savior and the guidance of all things on earth for sparing my life throughout the period of my course at University of Ilorin.\\

And also to my late Dad Alhaji J. A. Odebunmi, you are still in my heart and I miss your absence. May God forgive all your shortcomings and grant you eternal rest.

\newpage
\begin{center}\section*{Acknowledgments} \end{center}
To God be the glory, honor and adoration unto unchangeable God for his incomparable love and unspeakable grace upon my life during the period of this project work and for his protection over me throughout my stay on Better By Far campus.

In fact without God, assistance I wouldn't have achieved much, I am indeed very grateful for his providence and sustenance.\\

An adage says "towards every successful man there is an individual or group of individuals who contributes in one way or the other in order to achieve his good intention".\\

My sincere gratitude goes to my amiable supervisor; Dr O. T. Olotu for his assistance, advice and roles played in making this fruit of my educational endeavor a success. I owe him a lot for his patience, understanding and for his invaluable suggestions. May God almighty bless you and your entire family, sir\\

A sincere appreciation goes to my dearest H.O.D., Prof. K. Rauf for his support and counsel. May God almighty continue to bless your ways, sir.\\

I also want to acknowledge my level adviser; Dr (Mrs) I.F. Usamot, for her every-time support and her immeasurable word of encouragement during my stay on Better By Far campus. May God bless you and your home, ma.\\

A well deserving honour and gratitude to my lecturers; Prof. J. A. Gbadeyan, Prof. T. O. Opoola, Prof. O. M. Bamigbola, Prof. M. O. Ibrahim, Prof. O. A. Taiwo, Prof. R. B. Adeniyi, Prof. K. O. Babalola, Prof. M. S. Dada, Prof. A. S. Idowu, Dr E. O. Titiloye, Dr O. A. Fadipe-Joseph, Dr Y. O. Aderinto, Dr. C. N. Ejieji, Dr B. M. Yisa, Dr J. U. Abubakar, Dr K. A. Bello, Dr G. N. Bakare, Dr B. M. Ahmed, Dr O. A. Uwaheren, Dr O. odetunde, Dr T. L. Oyekunle, Dr A. A. Yeketi and all non-teaching staff of the department of Mathematics, University of Ilorin, for their useful and helpful contribution towards the completion of my academic career. May God Almighty guide you and bless your home all.\\

To my jewel of inestimable value, Mrs A. A. Odebunmi. Even with the absence of my Dad, you still stood firm in that position. I am greatly indebted to you for your sacrifice, care, guidance, advice, spiritual and financial support over me. I beseech Allah to bless you, guide you, answer all your prayers, spare your life for greatness on the right path and let you reap the fruit of your labor.\\ 

My profound gratitude goes to my siblings, Mr Saheed Odebunmi, Mrs, Moridiyah Odebunmi, Miss Wakilah Odebunmi, Mrs kafilah Odebunmi and to the entire Odebunmi's family. Thank you all for your love, care and support so far. I love you all and i pray Almighty Allah pave ways for us where seems no way.\\  

To Ilobu National Students' Union (INSU) where I am currently serving as National President. I appreciate you for giving me the opportunity to be the Chief Servant for the year 2021 and also to NAPHSS Unilorin Chapter where I am as well serving as the Speaker of the House and all other associations that I belong to, I am indebted to you all.\\

To the friends who Better By Far gave me, Salawudeen Jamiu Opeyemi, Ramon Halim Oyebamiji, Anifowowse Abdulkabir Adeola, Adeboye Musa Adisa, Saidu Hussein, Muhammed Yusuff and Olarinoye Temitope David. I'm very grateful to God for giving me friends like you and I as well appreciate you all. May we live to celebrate ourselves in the nearest future.\\

Finally, my warmest appreciation goes to everyone who has in one way or the other contributed to the success of my academic pursuit on Better By Far campus. I am very grateful to you all. Thanks to you all.	 

\newpage
\section*{\begin{center}ABSTRACT\end{center}}  
This research work is concerned with the application of Gaussian elimination to linear system of equations. Cholesky decomposition method is also applied for sake of establishing which of the two methods is the most accurate. The results reveal that Gaussian elimination method performs better than Cholesky decomposition method.
