\documentclass[a4paper 12pt]{report}

\newcommand{\bt}[1]{\textbf{#1}}
\newcommand{\ubt}[1]{\textbf{\underline{#1}}}
\newcommand{\sps}{\\[0.2cm]}
\newcommand{\spn}[1]{\\[#1cm]}
\newcommand{\refn}[1]{\textbf{(\ref{#1})}}
\newcommand{\NI}{\noindent}
\newcommand{\dsp}{\displaystyle}

\begin{document}
	\chapter*{REFERENCES}
	\addcontentsline{toc}{chapter}{REFERENCES}

		\NI Andreas, A., \& Wu-Sheng, L. (2007). \textit{Practical Optimization, Algorithm and Engineering Applications.}\sps
		
		\NI Avriel \& Mordecai, (2003). \textit{Nonlinear Programming: Analysis and Methods}. Dover Publishing. ISBN 0-486-43227-0.\sps
		
		\NI Bonnans, Frédéric J., Gilbert, Charles J., Lemaréchal, Claude, Sagastizábal, \& Claudia A. (2006). \textit{Numerical Optimization: Theoretical and Practical Aspects.} University text (Second revised ed. of translation of 1997 French ed.).\sps
		
		\NI Boyd, S., \& Vandenberghe, L. (2004). \textit{Convex Optimization}. Cambridge University Press.\sps
		
		\NI Fletcher, R., \& Reeves, C.M. (1964). \textit{Function Minimization by Conjugate Gradients}. Computer Journal.\sps
		
		\NI Fletcher, R. (1997). \textit{Practical Methods of Optimization (2nd ed.)}. New York: John Wiley \& Sons. ISBN 978-0-471-91547-8.\sps
		
		\NI Givens, Geof H., Hoeting, \& Jennifer, A. (2013). \textit{Computational Statistics}. Hoboken, New Jersey: John Wiley \& Sons. pp. 24–58. ISBN 978-0-470-53331-4.\sps
		
		\NI Kovalev, Dmitry, Mishchenko, Konstantin, Richtárik, \& Peter (2019). \textit{"Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates"}.\sps
		
		\NI Nocedal, Jorge, Wright, \& Stephen J. (1999). \textit{Numerical Optimization}. Springer-Verlag. ISBN 0-387-98793-2.\sps
		
		\NI Singireu, S.R. (2009). \textit{Engineering Optimization. Theory and Practical (4th ed.)}.\sps

\end{document}